Meta-analysis

### 2020-06-03 04_MetaAnalysis.Rmd
More code descriptions and description of hetrogeneity in the model

```{r Metafor-analysis}
PM_mv_AI <- rma.mv(
   yi,
   vi,
   mods = ~ spray_management,
   method = "ML",
   random = list(~ spray_management | trial),
   struct = "UN",
   data = slimmer_PM_dat
)

summary(PM_mv_AI)
```

```{r Initiak_ReRunMetafor, eval=FALSE, include=FALSE}
dat1 <- data.frame(
   iteration = 0,
   mods = names(coef(PM_mv_AI)),
   coefs = coef(PM_mv_AI),
   se = PM_mv_AI$se,
   zval = PM_mv_AI$zval,
   pval = PM_mv_AI$pval,
   ci.lb = PM_mv_AI$ci.lb,
   ci.ub = PM_mv_AI$ci.ub,
   row.names = NULL
   )

@@

```{r run_iterations_asJobscript, eval=FALSE, include=FALSE}
# WARNING don't run a high number of iterations without increasing sys.sleep
# sys.sleep should not be reduced below 4 for 50 iterations and
# below 0.5 for 10 iterations
for(ITERATE in 1:10){
rstudioapi::jobRunScript(
  "./R/ReRun_metafor-grainyield.R",
  workingDir = here::here(),
  name = "metafor_iteration",
)
   Sys.sleep(1)
}
```

```{r coef_iteration}
change_labels <- function(x1){
   x1 <- gsub(pattern = "spray_management",replacement = "",x = x1)
   x1 <- gsub(pattern = "_",replacement = "\n",x = x1)
   x1
}

dat1 <- read.csv("./cache/metaIteration.csv")
dat1 %>%
   ggplot(aes(x = iteration ,y = coefs,))+
   geom_ribbon(aes(ymax = ci.ub, ymin = ci.lb, x = iteration), fill = "grey70")+
   geom_line()+
   facet_grid(cols = vars(mods), labeller = labeller(mods = change_labels))+
   theme(strip.text.x = element_text(size = 9))

@@

```{r pval_iteration_plot}
dat1 %>%
   ggplot(aes(x = iteration ,y = pval,))+
   geom_line()+
   scale_y_log10()+
   geom_hline(yintercept = 0.05, colour = "grey50", linetype = 2)+
   facet_grid(cols = vars(mods), labeller = labeller(mods = change_labels))+
   theme(strip.text.x = element_text(size = 9))

temp_labels(dat1)
labeller()
```

>>>>

```{r Metafor-analysis}
PM_mv_AI <- rma.mv(
   yi,
   vi,
   mods = ~ spray_management,
   method = "ML",
   random = list(~ spray_management | trial),
   struct = "UN",
   data = slimmer_PM_dat
)
```

#### Investigate impact of imputing Mean square errors on the meta-analysis outcomes

```{r Initiak_ReRunMetafor, eval=FALSE, include=FALSE}
# It was noticed that the meta analysis was giving different outcomes.
#     (not just small variations in estimates and p-values, but large variations)
# The following chunks investigate how much these values vary and change the outcomes
#
# This chunk creates a data.frame from the meta-analysis which was run in the previous chunk `Metafor-analysis`
# and sets the iteration number as 0
# this data.frame is appended with additional iterations to in the following chunk

summary(PM_mv_AI)

dat1 <- data.frame(
   iteration = 0,
   mods = names(coef(PM_mv_AI)),
   coefs = coef(PM_mv_AI),
   se = PM_mv_AI$se,
   zval = PM_mv_AI$zval,
   pval = PM_mv_AI$pval,
   ci.lb = PM_mv_AI$ci.lb,
   ci.ub = PM_mv_AI$ci.ub,
   row.names = NULL
)

@@

```{r run_iterations_asJobscript, eval=FALSE, include=FALSE}
# This chunk iterates the imputation of MSEs and reruns the metafor analysis
# each time it iterates it appends some of the output information into the "metaIteration.csv" file
# To increase the speed the calculations/iterations it is send to multiple jobs in the background.
#
# WARNING don't run a high number of iterations without increasing sys.sleep
# sys.sleep should not be reduced below 4 for 50 iterations and
# below 0.5 for 10 iterations
for (ITERATE in 1:10) {
   rstudioapi::jobRunScript(
      "./R/ReRun_metafor-grainyield.R",
      workingDir = here::here(),
      name = "metafor_iteration",
   )
   Sys.sleep(1)
}
```

```{r coef_iteration, eval=FALSE, include=FALSE}
# This chunk plots the coefficients and corresponding confidence intervals 
#     for each iteration of the metafor calculation to visualise how much variation 
#     the imputed MSE imbue on the moderator coefs

# This function alters the moderator names so they are plotted legibly in the facet strips
change_labels <- function(x1){
   x1 <- gsub(pattern = "spray_management",replacement = "",x = x1)
   x1 <- gsub(pattern = "_",replacement = "\n",x = x1)
   x1
}

metaI <- read.csv("./cache/metaIteration.csv")
metaI %>%
   ggplot(aes(x = iteration ,y = coefs,))+
   geom_ribbon(aes(ymax = ci.ub, ymin = ci.lb, x = iteration), fill = "grey70")+
   geom_line()+
   facet_grid(cols = vars(mods), labeller = labeller(mods = change_labels))+
   theme(strip.text.x = element_text(size = 9)) # change facet strip label font size

@@

```{r pval_iteration_plot}
# Plot the p - values of the spray_management moderators
# transform y axis on log scale
metaI %>%
   ggplot(aes(x = iteration , y = pval, )) +
   geom_line() +
   scale_y_log10() +
   geom_hline(
      yintercept = c(0.05, 0.001),
      colour = "grey50",
      linetype = 2
   ) +
   facet_grid(cols = vars(mods),
              labeller = labeller(mods = change_labels)) +
   theme(strip.text.x = element_text(size = 9)) +
   geom_text(
      aes(
         y = 0.05,
         x = 1,
         label = c("P = 0.05")
      ),
      size = 3,
      colour = "grey50",
      hjust = 0,
      vjust = -0.5
   )+
      geom_text(
      aes(
         y = 0.001,
         x = 1,
         label = c("P = 0.001")
      ),
      size = 3,
      colour = "grey50",
      hjust = 0,
      vjust = -0.5
   )

```{r metafor_summary}
summary(PM_mv_AI)
rstudent.rma.mv(PM_mv_AI)
# confint(PM_mv_AI) Can't finish running
```

According to the results of the omnibus test ($Q_M = 10.65, df = 4, p = 0.0308$) we can reject the null hypothesis $H_0 : \beta_1 = \beta_2 = \beta_3 =\beta_4 = 0$ that the tested spray management schedules have no benefit to protecting mungbean yields[@Viechtbauer2010]. 
However Late plus ($\beta_4$) was the only moderator showing a significant effect on yields ($z = 3.2276; p = 0.0012$). 
The analysis shows there is still a considerable amount of residual heterogeneity ($Q_E = 5096.04, df = 125, p < 0.0001$) not captured by the spray management moderator indicating other possible moderators which might influence grain yield.
